Target Markdown

### 2022-09-02 _targets.Rmd
edited pipeline

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite"))#,
    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
    # 
)
```

@@

     tar_target(matching, match(db_path, ids)
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

@@

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(db_path),
     #           format = "qs")

>>>>

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path, nrows = 20),
              format = "qs"),
     tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))#,

    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs", pattern = map(ids_complete_vector), iteration = "list")
    # 
)
```

@@

     tar_target(matching, match(db_path, ids),
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")

@@

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(db_path),
     #           format = "qs")
